Supporting Information: Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2020-01-09 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Fixed figure references

  We evaluated the predictive capabilities of the AD modeling approach by training
  the model parameters on the first half of the equilibrated MD trajectory data and
  then comparing the MSD calculated from AD model realizations to the MSD calculated
  from the second half of the equilibrated MD trajectory data. This metric is
  only meaningful if the ensemble of solute trajectories is stationary. In 
  Figure~\ref{msd_comparison}, we show that urea and acetic acid show acceptable
  stationary behavior while methanol and ethylene glycol do not.

@@

  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
  because the Hurst parameter is challenging to quantify, especially with a relatively 
  small amount of data (see Section~\ref{method:sfbm} for further discussion of this 
  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
  but also lower the predicted MSD meaning we are either underestimating the width of
  the hop length distribution, favoring longer dwell times, or both.

@@

>>>>

  We evaluated the predictive capabilities of the AD modeling approach by training
  the model parameters on the first half of the equilibrated MD trajectory data and
  then comparing the MSD calculated from AD model realizations to the MSD calculated
  from the second half of the equilibrated MD trajectory data. This metric is
  only meaningful if the ensemble of solute trajectories is stationary. In 
  Figure~\ref{fig:msd_comparison}, we show that urea and acetic acid show acceptable
  stationary behavior while methanol and ethylene glycol do not.

@@

  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
  because the Hurst parameter is challenging to quantify, especially with a relatively 
  small amount of data (see Section~\ref{M-method:sfbm} of the main text for further discussion of this 
  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
  but also lower the predicted MSD meaning we are either underestimating the width of
  the hop length distribution, favoring longer dwell times, or both.

@@

  The value of $\beta$ for the MSDDM is under-estimated due to assumptions of the model
  itself as well as inaccuracies in the correlation structure of very long FLM trajectories.
  Turning first to the model itself, we have designed it to ensure that the magnitude of the
  hops in the series of transitions between states are anti-correlated from start to finish. 
  This assumes that the transition correlation structure is unaffected by the
  sub-trajectories between each state transition. Each time a state transition occurs, one
  must initialize a new time series sub-trajectory with its own correlation structure. 
  %Even with a low Hurst parameter, as exhibited by most trapped states, the time spent 
  %in each state is relatively short making the accuracy of the correlation structure 
  %questionable. Additionally, $\sigma$ of transitional hops is similar in magnitude to
  %$\sigma$ in trapped states. 
  Since we add the transitional hop lengths to each end of
  trapped state sub-trajectories, the transitional hop lengths are shifted with respect 
  to one another, decreasing correlation between them. We tested this reasoning by modifying the 
  MSDDM to completely immobilize particles except when they transition between states. 
  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 
  reveals that this is actually a consequence of the FLM simulation procedure. Simulating
  FLM requires Riemann-sum approximations of the stochastic integrals defining the process.
  To generate the curves in Figure~\ref{M-fig:flux_curves_msddm}, we needed to correlate 
  25--1000 times more hops than for the MSD predictions in Figure~\ref{M-fig:msddm_performance}. 
  In short, it is computationally infeasible to use enough terms to accurately incorporate
  long timescale correlations into our long MSDDM realizations. Thus at long timescales, 
  we lose correlation between transitional jumps. We confirmed this hypothesis by using 
  fractional Brownian motion, for which we have an exact simulation method, in place of 
  FLM in the MSDDM algorithm. When we use FBM, $\beta$ increases well above the Brownian 
  value. $\beta$ increases even further if we immobilize the trapped states. Thus the low
  value of $\beta$ of the MSDDM is a consequence of model assumptions and inexact simulation
  of FLM.
